\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 implementation.tex
.

\begin{table}[!htbp]
\centering
\caption{Avg. timings for benchmarks. The \textbf{BMC} column lists
time taken by the BMC engine. The total time in seconds (rounded off
to an integer) is noted under \textbf{S3CAM-R} and \textbf{S3CAM}.
$TO$ signifies time $>5hr$, after which the search was killed.}
\label{tab:res-rel}
\begin{tabular}{@{}llll@{}}
\toprule
    Benchmark & PWA Rel + BMC & PWA Rel + LP & S3CAM\\
\midrule
    Van der Pol ($\prop_3$)   &$14$ & $20$ & $24$\\
    Brusselator               &$4$ & $4$ & $2$\\
    Lorenz                    &$122$ & $120$ & $35$\\
%B.Ball                    &  &   & \\
    Nav ($\prop_P$)           &$TO$ & $1710$  & $603$ \\%9423 + 4480
    Nav ($\prop_Q$)           &$TO$ & $1560$   & $546$ \\%8105 + 970
    Nav ($\prop_R$)           &$TO$ & $2352$  & $2003$\\
    Nav ($\prop_S$)           &$TO$ & $0$  & $2100$\\
    Bouncing Ball             &$TO$ & $0$  & $450$\\

>>>>

\begin{table}[!htbp]
\centering
\caption{Avg. timings for benchmarks. The \textbf{BMC} column lists
time taken by the BMC engine. The total time in seconds (rounded off
to an integer) is noted under \textbf{S3CAM-R} and \textbf{S3CAM}.
$TO$ signifies time $>5hr$, after which the search was killed.}
\label{tab:res-rel}
\begin{tabular}{@{}llll@{}}
\toprule
    Benchmark & PWA Rel + BMC & PWA Rel + LP & S3CAM\\
\midrule
    Van der Pol ($\prop_3$)   &$14$ & $20$ & $24$\\
    Brusselator               &$4$ & $4$ & $2$\\
    Lorenz                    &$122$ & $120$ & $35$\\
%B.Ball                    &  &   & \\
    Nav ($\prop_P$)           &$TO$ & $1710$  & $603$ \\%9423 + 4480
    Nav ($\prop_Q$)           &$TO$ & $1560$   & $546$ \\%8105 + 970
    Nav ($\prop_R$)           &$TO$ & $2352$  & $2003$\\
    Nav ($\prop_S$)           &$TO$ & $0$  & $2100$\\
    Bouncing Ball             &$Safe$ & $Safe$  & $450$\\
